Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-13 doc/main_jfm.tex
modified main_jfm.tex for new figures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider an $N_b$-many body collection of Janus particles suspended
in a two-dimensional unbounded domain $\Omega$. The boundary of each
particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup
\Gamma_2 \cup \cdots \cup \Gamma_{N_b}$. Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is the constant viscosity, $p$ is the
pressure, and $\uu_\infty$ is the background flow. Since each particle
$\Gamma_i$ with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu_i$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

@@

We have the following jump relations for \eqref{eq:uidef}: 
\begin{equation}
\label{eq:DLjump}
\jump{u_i} = \sigma, \quad
\jump{v_i} = 0, \quad
\jump{\nabla u_i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
\jump{\nabla v_i} = \mathbf{0},
\end{equation}
on $\Gamma_i$. Therefore,
\begin{align*}
  \jump{{\bf T}_2\nnu}   &= \jump{\mathbf{S}(u_i,v_i)\nnu  +\mathbf{S}(v_i,u_i)\nnu} \\
  &= \jump{( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
- 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla u_i^T)  \nnu}\\
&= 2\gamma\rho^{-1} \sigma v_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dv_i }{ds} \nnu
- 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dv_i }{d\nu} \ttau = \JJ_i.
\end{align*}
Combing this with~\eqref{eq:prejump} gives~\eqref{eq:recipforcetorque}
as required.

@@

\subsection{Self-Assembly and Relaxation}
\begin{figure}
\centering
\includegraphics[height=2in]{relax2.eps}
\includegraphics[height=2in]{relax.eps}\\
\includegraphics[height=2.in]{N58_0pres.pdf}
\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
\caption{\label{figure2} A JP Vesicle relaxing under a quiescent flow.
  (a) The blue dashed and solid curves are mean magnitudes of the
  particle velocities in $x$ and $y$ directions, respectively. The red
  curve shows the decreasing trend of the mean magnitude of particle
  orientation change. The black dashed line shows the reference of how
  all magnitudes decay. (b) Bilayer configurations for $t=0$ (black) and
  $t=1000$ (red) with particle directors. (c)--(d) show the fluid
  pressure profiles for $t=0$ and $t=1000$ where the background curves
  indicate the streamlines. In panel (c), the pressure value in internal
  fluid is much higher than the pressure outside of the bilayer. After
  the JP vesicle relaxes, this immersed permeable bilayer approaches the
  steady state shown in panel (d).}
\end{figure}

@@

\begin{figure}
\centering
  \todo[inline]{The left figure is shorter than the other 2}
\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
  \caption{\label{figure:permeability} JP vesicles are suspended in a
  quiescent flow for relaxations where the reference arc lengths $L_0$
  are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm,
  $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$
  decreases over time where the dashed curves represent the data and
  solid curves are linear fits; (b) A linear relationship between
  $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear
  relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels
  (b) and (c), the cross and asterisk symbols are numerical results and
  fitted by using solid lines.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_0.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{\label{figure3} A JP vesicle suspended in a shear flow with
  shear rate $\chi=0.0025$. (a) The initial configuration of a 58-body
  JP vesicle where the black arrows point in the direction of the
  hydrophobic side of the JP. (b) The particle velocities and
  streamlines of the configuration in (a). The streamlines are plotted
  in the background as solid curves and the red arrows represent the
  particle velocities. (c) The deformed tank-treading JP vesicle at
  $t=4000$. (d) The particle velocities and streamlines of the
  configuration in (c). The background colors in panels (a) and (c)
  represent the strength of the hydrophobic attraction potential. The
  blue regions have the weakest action and the red regions in the
  bilayer have the strongest action.}
\end{figure}
%

@@

\begin{figure}
\begin{center}
\hspace{-0.6cm}
\includegraphics[height=2in]{ReducedArea.pdf}
\hspace{0.6cm}
\includegraphics[height=2in]{DecayRate.eps}\\
\includegraphics[height=2in]{ArcLength.pdf}
\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4} (a) The reduced area transitioning over time
  for four different shear rates. The smooth curves are a best-fit
  exponential curve. (b) The decay rate $k$, using the exponential fit
  to the data in panel (a), for a number of shear rates. The inset shows
  the terminal reduced areas. (c) The total arc lengths of the midplanes
  over time for four shear rates. (d) The excess length of the
  midplanes. For all panels, a set of shear rates
  $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. The
  legend in panel (d) applies to both panels (a) and (c).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle suspended in a parabolic flow
  where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
  20$~nm, and the control parameter is $w=25$~nm. The configuration is
  the state when $t=\{0, 4000, 8000\}$ which correspond to $0\ \mu $s, $2.44\ \mu $s, and $4.88\ \mu $s. The red curves are the midplanes. Inter-monolayer slip is observed by comparing the relative  locations of the blue and yellow particles.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{parabolic.eps}
  \caption{\label{figure7} The schematic of a JP vesicle suspended in a
  parabolic flow where the strength of the flow is
  $v_{max}=32.8$~nm~ns$^{-1}$, $R_0 = 20$~nm, and the control parameter
  is $w=25$~nm. The configuration occurs when $t=6.1\ \mu$s and red arrows indicate the tank-treading motion. The inset plots the trajectory of mean $y$-position over time.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{N58_rupt_0.pdf}
\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
\includegraphics[height=2in]{N58_rupt_400.pdf}
\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Membrane rupture occurs when the shear rate
  exceeds a threshold. Here the shear rate is $\chi = 0.1$. Starting
  with a circular shape (panel (a)), the vesicle is stretched by the
  background flow and multiple pores form (panel (b)). Panels (c)--(d)
  show the later states during the simulation. Streamlines are included
  in each panel.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{N116_shear_0.pdf}
\includegraphics[height=2in]{N116_shear_2500.pdf}\\
\includegraphics[height=2in]{N116_shear_5000.pdf}
\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{\label{figure10} Two JP vesicles suspended in a shear flow
  where the dimensioneless shear rate is $\chi=0.005$. The initial
  configuration is shown in panel (a). Panels (b)-(d) represent configurations when $t = \{500, 1000, 1500\}$.
  The background color is the fluid
  pressure. The color bar is identical for all panels. Streamlines are
  plotted in purple. The insets of all panels are generated from
  simulations of a continuum model of the vesicles and the streamlines
  agree between the two models. }
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{N116_ext_0.pdf}
\includegraphics[height=2in]{N116_ext_2000.pdf}\\
\includegraphics[height=2in]{N116_ext_4000.pdf}
\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{\label{figure12} Two JP vesicles suspended in an
  extensional flow where the dimensioneless extensional rate is
  $\chi=0.005$. The centroid of the left JP vesicle is $0.1$ units
  above the $x$-axis and the centroid of the right JP vesicle is
  $0.1$ units below the $x$-axis. The initial configuration is shown in
  panel (a). Panels (b)-(d) represent configurations when $t = \{400, 800, 1300\}$. 
  The background color is the fluid pressure. The color bar
  is identical for all panels. Streamlines are plotted in purple. The
  insets of all panels are generated from simulations of a continuum
  model of the vesicles and the streamlines agree between the models.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\begin{center}
\includegraphics[width=11.32cm]{Figure0_Wrapper.pdf}
\end{center}
\caption{The diagram illustrates the domain and boundary conditions for the mobility problem formulation.}
\label{fig:figure0}
\end{figure}

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
We consider an $N_b$-many body collection of Janus particles suspended
in a two-dimensional unbounded domain $\Omega$. The boundary of each
particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup
\Gamma_2 \cup \cdots \cup \Gamma_{N_b}$. Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is the constant viscosity, $p$ is the
pressure, and $\uu_\infty$ is the background flow. Since each particle
$\Gamma_i$ with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu_i$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

@@

We have the following jump relations for \eqref{eq:uidef}: 
\begin{equation}
\label{eq:DLjump}
\jump{u_i} = \sigma, \quad
\jump{v_i} = 0, \quad
\jump{\nabla u_i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
\jump{\nabla v_i} = \mathbf{0},
\end{equation}
on $\Gamma_i$. Therefore,
\begin{align*}
  \jump{{\bf T}_2\nnu}   &= \jump{\mathbf{S}(u_i,v_i)\nnu  +\mathbf{S}(v_i,u_i)\nnu} \\
  &= \jump{( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
- 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla u_i^T)  \nnu}\\
&= 2\gamma\rho^{-1} \sigma v_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dv_i }{ds} \nnu
- 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dv_i }{d\nu} \ttau = \JJ_i.
\end{align*}
Combining this with~\eqref{eq:prejump} gives~\eqref{eq:recipforcetorque}
as required.

@@

\subsection{Self-Assembly and Relaxation}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure1_Wrapper.pdf}
%\includegraphics[height=2in]{relax2.eps}
%\includegraphics[height=2in]{relax.eps}\\
%\includegraphics[height=2.in]{N58_0pres.pdf}
%\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
\caption{\label{figure2} A JP Vesicle relaxing under a quiescent flow.
  (a) The blue dashed and solid curves are mean magnitudes of the
  particle velocities in $x$ and $y$ directions, respectively. The red
  curve shows the decreasing trend of the mean magnitude of particle
  orientation change. The black dashed line shows the reference of how
  all magnitudes decay. (b) Bilayer configurations for $t=0$ (black) and
  $t=1000$ (red) with particle directors. (c)--(d) show the fluid
  pressure profiles for $t=0$ and $t=1000$ where the background curves
  indicate the streamlines. In panel (c), the pressure value in internal
  fluid is much higher than the pressure outside of the bilayer. After
  the JP vesicle relaxes, this immersed permeable bilayer approaches the
  steady state shown in panel (d).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
%\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
%\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
%\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
  \caption{\label{figure:permeability} JP vesicles are suspended in a
  quiescent flow for relaxations where the reference arc lengths $L_0$
  are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm,
  $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$
  decreases over time where the dashed curves represent the data and
  solid curves are linear fits; (b) A linear relationship between
  $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear
  relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels
  (b) and (c), the cross and asterisk symbols are numerical results and
  fitted by using solid lines.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=11.5cm]{Figure3_Wrapper.pdf}
%\includegraphics[width=0.3\textwidth]{N58_0.pdf}
%\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
%\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
%\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{\label{figure3} A JP vesicle suspended in a shear flow with
  shear rate $\chi=0.0025$. (a) The initial configuration of a 58-body
  JP vesicle where the black arrows point in the direction of the
  hydrophobic side of the JP. (b) The particle velocities and
  streamlines of the configuration in (a). The streamlines are plotted
  in the background as solid curves and the red arrows represent the
  particle velocities. (c) The deformed tank-treading JP vesicle at
  $t=4000$. (d) The particle velocities and streamlines of the
  configuration in (c). The background colors in panels (a) and (c)
  represent the strength of the hydrophobic attraction potential. The
  blue regions have the weakest action and the red regions in the
  bilayer have the strongest action.}
\end{figure}
%

@@

\begin{figure}
\begin{center}
\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
%\hspace{-0.6cm}
%\includegraphics[height=2in]{ReducedArea.pdf}
%\hspace{0.6cm}
%\includegraphics[height=2in]{DecayRate.eps}\\
%\includegraphics[height=2in]{ArcLength.pdf}
%\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4} (a) The reduced area transitioning over time
  for four different shear rates. The smooth curves are a best-fit
  exponential curve. (b) The decay rate $k$, using the exponential fit
  to the data in panel (a), for a number of shear rates. The inset shows
  the terminal reduced areas. (c) The total arc lengths of the midplanes
  over time for four shear rates. (d) The excess length of the
  midplanes. For all panels, a set of shear rates
  $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. The
  legend in panel (d) applies to both panels (a) and (c).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
%\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle suspended in a parabolic flow
  where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
  20$~nm, and the control parameter is $w=25$~nm. The configuration is
  the state when $t=\{0, 4000, 8000\}$ which correspond to $0\ \mu $s, $2.44\ \mu $s, and $4.88\ \mu $s. The red curves are the midplanes. Inter-monolayer slip is observed by comparing the relative  locations of the blue and yellow particles.}
\end{figure}

\begin{figure}
\centering
%\includegraphics[height=2in]{parabolic.eps}
  \caption{\label{figure7} The schematic of a JP vesicle suspended in a
  parabolic flow where the strength of the flow is
  $v_{max}=32.8$~nm~ns$^{-1}$, $R_0 = 20$~nm, and the control parameter
  is $w=25$~nm. The configuration occurs when $t=6.1\ \mu$s and red arrows indicate the tank-treading motion. The inset plots the trajectory of mean $y$-position over time.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Membrane rupture occurs when the shear rate
  exceeds a threshold. Here the shear rate is $\chi = 0.1$. Starting
  with a circular shape (panel (a)), the vesicle is stretched by the
  background flow and multiple pores form (panel (b)). Panels (c)--(d)
  show the later states during the simulation. Streamlines are included
  in each panel.}
\end{figure}

@@

\begin{figure}
  \centering
\includegraphics[width=\textwidth]{Figure10_Wrapper.pdf}  
%\includegraphics[height=2in]{N116_shear_0.pdf}
%\includegraphics[height=2in]{N116_shear_2500.pdf}\\
%\includegraphics[height=2in]{N116_shear_5000.pdf}
%\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{\label{figure10} Two JP vesicles suspended in a shear flow
  where the dimensioneless shear rate is $\chi=0.005$. The initial
  configuration is shown in panel (a). Panels (b)-(d) represent configurations when $t = \{500, 1000, 1500\}$.
  The background color is the fluid
  pressure. The color bar is identical for all panels. Streamlines are
  plotted in purple. The insets of all panels are generated from
  simulations of a continuum model of the vesicles and the streamlines
  agree between the two models. }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Figure12_Wrapper.pdf}
%\includegraphics[height=2in]{N116_ext_0.pdf}
%\includegraphics[height=2in]{N116_ext_2000.pdf}\\
%\includegraphics[height=2in]{N116_ext_4000.pdf}
%\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{\label{figure12} Two JP vesicles suspended in an
  extensional flow where the dimensioneless extensional rate is
  $\chi=0.005$. The centroid of the left JP vesicle is $0.1$ units
  above the $x$-axis and the centroid of the right JP vesicle is
  $0.1$ units below the $x$-axis. The initial configuration is shown in
  panel (a). Panels (b)-(d) represent configurations when $t = \{400, 800, 1300\}$. 
  The background color is the fluid pressure. The color bar
  is identical for all panels. Streamlines are plotted in purple. The
  insets of all panels are generated from simulations of a continuum
  model of the vesicles and the streamlines agree between the models.}
\end{figure}
